On the Design, Use and Removal of Eval in R

### 2020-08-20 inst/paper/main.tex
Add some details

- cannot replace with (cite study of with construct).
\textbf{*}

\section{Background on R}
\textbf{Aviral}

\section{The Design of Eval}
\textbf{Aviral}

\section{Infrastructure}
\textbf{Aviral + Filip}

\section{Corpus of R Programs}
\textbf{Filip}

\section{Threats to Validity}
\textbf{Filip}

\section{Analyzing Eval Usage Patterns}
This section presents the results of our empirical study of eval in the R language.
\subsection{How many evals}
\textbf{Pierre}

\subsection{How are they used}
\textbf{Pierre}
- classify evals based on what they can be replaced with

\subsection{How to replace evals}
\textbf{Aviral}

\subsection{How many evals can be replaced}
\textbf{Aviral}

\section{Evaluation}

@@

>>>>

- cannot replace with (cite study of with construct).
- 
\textbf{*}

\section{Background on R}
- Talk about environments
- How is it different from JS (takes language, env in R but string in JS).

\section{The Design of Eval}

\section{Infrastructure}

\section{Corpus of R Programs}

\section{Threats to Validity}

\section{Research Question}
This section presents the results of our empirical study of eval in the R language.
\subsection{How many evals}

\subsection{How are they used}

- classify evals based on what they can be replaced with

\subsection{How to replace evals}

\subsection{How dangerous is eval}

\subsection{How many evals can be replaced}

@@

Eval is evil, we would like to replace it.
Research Questions
How often is eval used? 
How often it is used in base / other packages?
blocking: cannot find out precisely what comes from base
What is the source of evals?
Provenance (source arguments to eval)
How many evals are in libraries / vignettes
What is eval used for?
??Eval in the tidyverse
TODO: Classification of evals in  packages (Pierre)
TODO: look at the first function to get
binary / unary / assignment / other function
does it have {
evals that do nothing (they get values)
...
TODO: In the case of base package (Filip)
access default values of formals
simply implementation
weird replacement of calls (write.csv -> write.table)
accessing variable from another environment (instead of get)
evaling user input
Change of caller pattern: 
m <- match.call()
 m$name <- NULL
 m[[1L]] <- as.name("library")
eval(m, .GlobalEnv)
     - 	TODO: How dangerous is eval? (Aviral)
Does eval generate new code (create new functions)?
environment writes (reads)
system environment variables
connections
random number generator - setting seed
Does eval do dynamic code loading?
Does eval argument reflect on the call stack?
Calls to C Code
TODO: Could the eval be made safer?
TODO: Could some of the eval calls be replaced?
